---
title: "p8105_hw5_dz2399"
author: "DZ"
date: "November 1, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
```

## Creating a dataset
```{r,message=F}
files_name <- list.files('./data1')

read_df <- function(x){
  df <- read_csv(paste0('./data1/',x))
  df}

id <- files_name %>% 
  str_replace('.csv','') %>%
  str_split('_',simplify = T)                                                         
colnames(id) <- c('arm','subject_id')
id <- mutate(as.tibble(id), subject_id=as.numeric(subject_id))
  
df_all <- purrr::map(files_name,read_df) %>% 
  bind_rows(.id='id') 

df_all <- cbind(id,df_all) %>% 
  gather(key=week, value=value, week_1:week_8) %>% 
  mutate(week=str_replace(week, 'week_','')) %>% 
  mutate(week=as.numeric(week))

label <- c('con'='Control', 'exp'='Experiment')

ggplot(df_all, aes(x=week, y=value))+
  facet_grid(.~arm,labeller=as_labeller(label))+
  geom_line(aes(color=as.factor(subject_id)))+
  ggtitle('Observations on each subject over time')+
  theme(legend.position='bottom')
```

As the graph shows, the experiment group shows an increasing trend over time while the control group stays the same.


## Question 2
### Describing the homicide dataset
```{r, message=F}
df_homicide <- read_csv('./data2/homicide_data.csv') %>%
  janitor::clean_names()

```

The homicide dataset has the dimension of `r dim(df_homicide)[1]` rows and `r dim(df_homicide)[2]` columns. In the raw data, the character variables are uid, victim_last, victim_first, victim_race, victim_age, victim_sex, city, state, disposition. Numeric variables are lat and lon.

### Creating the city_state variable and summary tables
```{r}
df_homicide <- df_homicide %>%
  mutate(city_state = paste(city,state,sep = ',')) 

total_homi <- df_homicide %>% 
  group_by(city_state) %>% 
  summarise(total_homicide = n()) 

unsolved_homi <- df_homicide %>% 
  filter(disposition=='Closed without arrest'|disposition=='Open/No arrest') %>% 
  group_by(city_state) %>% 
  summarise(unsolved_homicide = n()) 


df_total_unsolved <- merge(total_homi,unsolved_homi,by='city_state') 

knitr::kable(df_total_unsolved)

```


## Baltimore unsolved proportion table
```{r,message=F}
baltimore <- df_total_unsolved %>% 
  filter(city_state=='Baltimore,MD')

p.test <- prop.test(baltimore$unsolved_homicide,baltimore$total_homicide) 

broom::tidy(p.test)[,c(1,5,6)]
```


### Iteration
```{r,message=F}
p_fun <- function(x){
p.test <- prop.test(x$unsolved_homicide,x$total_homicide) 
broom::tidy(p.test)[,c(1,5,6)]
}

df_all_prop <- nest(df_total_unsolved,total_homicide:unsolved_homicide) %>% 
     mutate(prop_result=map(data,p_fun)) %>% 
     unnest()
as.tibble(df_all_prop)
```

The plot of estimates and CIs for each city
```{r,message=F}
df_all_prop %>% 
  mutate(estimate=round(estimate,2)) %>% 
  ggplot(aes(x=reorder(city_state,-estimate),y=estimate))+
  geom_bar(stat = 'identity',alpha=.5)+
  geom_errorbar(mapping=aes(x=city_state, ymin=conf.low, ymax=conf.high), width=0.1, size=1, color="blue",alpha=.5)+
    coord_flip()+
  xlab('Cities')+
  ylab('Estimates with CI')
  ggtitle('The estimates and CIs for each city')

```

In this graph, we can observe that Chicago, Baltimore, New Orleans, are the top three cities of unsolved case proportions. 